\gettitle

### 2019-10-30 assignment1/submission1.tex
fix deltas in 1.2

\section*{2 System Models}
\subsection*{a)}
\begin{itemize}
	\item No message is lost
	\item The maximal possible delay is known
\end{itemize}
\subsection*{b)}
\subsubsection*{i.}
Every process i sends its own messages at time i * δt:
t\textsubscript{i}\textsuperscript{send}(m) = i * δt
The tranmission of a given message is not longer than δt, so if a process i starts sending after i * δt every process with a lower id has allready finished and all processes know there messages.
\subsubsection*{ii.}
The worst-case is n * δt as δt is reserved for every prozess as time to send und δt is the loangest time a prozess needs for transmitting a message

>>>>

\section*{2 System Models}
\subsection*{a)}
\begin{itemize}
	\item No message is lost
	\item The maximal possible delay is known
\end{itemize}
\subsection*{b)}
\subsubsection*{i.}
Every process i sends its own messages at time $ i * \delta t$:
t\textsubscript{i}\textsuperscript{send}(m) = $ i * \delta t $
The tranmission of a given message is not longer than $ \delta $t, so if a process i starts sending after i * $ \delta $t every process with a lower id has allready finished and all processes know there messages.
\subsubsection*{ii.}
The worst-case is n * $ \delta $t as $ \delta $t is reserved for every prozess as time to send und $ \delta $t is the loangest time a prozess needs for transmitting a message
